QRF Covariate Selection

### 2020-01-25 analysis/R_scripts/fit_qrf_model.Rmd
added to script to include capacity estimates where RST spawner-recruit data exists. Saved all objects in analysis/data/derived_data as .rds objects, rather than in R package data.

# save some results
usethis::use_data(fish_hab, 
                  hab_dict,
                  hab_data,
                  hab_avg,
                  sel_hab_mets,
                  qrf_data,
                  dens_offset,
                  qrf_mod,
                  version = 2,
                  overwrite = T)

@@

@@

```{r save-extrapolation}

usethis::use_data(gaa_covars,
                  mod_data_weights,
                  model_svy_df,
                  all_preds,
                  version = 2,
                  overwrite = T)

@@

>>>>

# save some results
# usethis::use_data(fish_hab, 
#                   hab_dict,
#                   hab_data,
#                   hab_avg,
#                   sel_hab_mets,
#                   qrf_data,
#                   dens_offset,
#                   qrf_mod,
#                   version = 2,
#                   overwrite = T)

write_rds(fish_hab,
          "../data/derived_data/fish_hab.rds")
write_rds(hab_dict,
          "../data/derived_data/hab_dict.rds")
write_rds(hab_data,
          "../data/derived_data/hab_data.rds")
write_rds(sel_hab_mets,
          "../data/derived_data/sel_hab_mets.rds")
write_rds(qrf_data,
          "../data/derived_data/qrf_data.rds")
write_rds(dens_offset,
          "../data/derived_data/dens_offset.rds")
write_rds(qrf_mod,
          "../data/derived_data/qrf_mod.rds")

@@

# for CHaMP sites, use direct QRF esimates, not extrapolation ones
all_preds %<>%
  left_join(mod_data %>%
              select(Site, 
                     qrf_chnk_per_m = chnk_per_m,
                     qrf_chnk_per_m2 = chnk_per_m2)) %>%
  mutate(chnk_per_m = if_else(!is.na(qrf_chnk_per_m),
                              qrf_chnk_per_m,
                              chnk_per_m),
         chnk_per_m_se = if_else(!is.na(qrf_chnk_per_m),
                                 as.numeric(NA),
                                 chnk_per_m_se),
         chnk_per_m2 = if_else(!is.na(qrf_chnk_per_m2),
                               qrf_chnk_per_m2,
                               chnk_per_m2),
         chnk_per_m2_se = if_else(!is.na(qrf_chnk_per_m2),
                                  as.numeric(NA),
                                  chnk_per_m2_se)) %>%
  select(-starts_with('qrf'))

@@

```{r save-extrapolation}
# usethis::use_data(gaa_covars,
#                   mod_data_weights,
#                   # model_svy_df,
#                   all_preds,
#                   version = 2,
#                   overwrite = T)

write_rds(gaa_covars,
          "../data/derived_data/gaa_covars.rds")
write_rds(mod_data_weights,
          "../data/derived_data/mod_data_weights.rds")
write_rds(model_svy_df,
          "../data/derived_data/model_svy_df.rds")
write_rds(all_preds,
          "../data/derived_data/all_preds.rds")

@@

# Validation

We validated our estimates by comparing them with selected areas that had spawner-recruit data available.

```{r}
library(sf)
data("chnk_domain")
# read in trap polygons
trap_poly = read_sf('../data/derived_data/trap_regions.shp') %>%
  # st_transform(crs = 5070)
  st_transform(st_crs(chnk_domain)) %>%
  select(-Id)

capacity_pts = all_preds %>%
  st_as_sf(coords = c('Lon', 'Lat'),
           crs = 4326) %>%
  st_transform(st_crs(chnk_domain))

qrf_caps = trap_poly %>%
  split(list(.$trap_name)) %>%
  map_df(.id = 'Trap',
         .f = calc_watershed_cap,
         spp_range = chnk_domain,
         capacity_pts = capacity_pts,
         capacity_name = "chnk_per_m",
         capacity_se_name = 'chnk_per_m_se') %>%
  mutate(tot_cap_cv = tot_cap_se / tot_cap) %>%
  mutate(Trap = recode(Trap,
                       'Minam R.' = 'Minam River',
                       'Entiat R.' = 'Entiat River',
                       'Crooked Fork Creek' = 'Crooked Fork',
                       'Upper Grande Ronde R.' ='Upper Grande Ronde River',
                       'Toucannon R.' = 'Tucannon River',
                       'Pahsimeroi' = 'Pahsimeroi River',
                       'Hood R.' = 'Hood River',
                       'John Day Middle Fork' = 'Middle Fork John Day',
                       'Upper Salmon River' = 'Upper Salmon River Chinook',
                       'John Day Upper Mainstem' = 'Upper Mainstem John Day',
                       'East Fork Salmon' = 'East Fork Salmon River',
                       'Lostine R.' = 'Lostine River'))

library(FSA)
bh1 <- srFuns('BevertonHolt',
              param = 3)

data("spawn_rec_data")
# fit Beverton-Holt curve with capacity fixed at QRF capacity prediction
qrf_params = spawn_recr_data %>%
  group_by(Population) %>%
  nest() %>%
  left_join(qrf_caps,
            by = c('Population' = 'Trap')) %>%
  filter(!is.na(tot_cap)) %>%
  mutate(form = 'QRF',
         inits = map2(.x = data,
                      .y = tot_cap,
                     .f = function(x, y) {
                       inits = srStarts(Parr ~ Spawners,
                                        data = x,
                                        type = 'BevertonHolt',
                                        param = 3)

                       inits$a = if_else(inits$a < 0, 
                                         2e-3, 
                                         inits$a)
                       inits$b = 1 / y
                       return(inits)
                       }),
         mod_fit = map2(.x = data,
                        .y = inits,
                        .f = function(x, y) {
                          fit = try(nls(log(Parr) ~ log(bh1(Spawners, a, b)),
                                        data = x,
                                        start = y,
                                        algorithm = 'port',
                                        lower = c(0, y['b']),
                                        upper = c(Inf, y['b'])))
                        }),
         coefs = map(mod_fit,
                     .f = function(x) {
                       if(class(x) == 'try-error') {
                         return(as.numeric(NA))
                       } else coef(x)
                       }),
         preds = map2(.x = data,
                      .y = mod_fit,
                      .f = function(x, y) {
                        if(class(y) != 'try-error') {
                          tibble(Spawners = 1:max(x$Spawners)) %>%
                            mutate(Parr = predict(y,
                                                  newdata = .),
                                   Parr = exp(Parr))
                        } else return(tibble(Spawners = NA,
                                             Parr = NA))
                      })) %>%
  rename(est = tot_cap,
         se = tot_cap_se) %>%
  select(-c(area:tot_length, tot_cap_cv)) %>%
  mutate(cv = se / est)

# combine with other spawner recruit estimates
data("spawn_rec_params")

spawn_rec_params %<>%
  bind_rows(qrf_params)

# save complete table
write_rds(spawn_rec_params,
          path = "../data/derived_data/spawn_rec_params.rds")
